---
title: "Report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plyr)
library(ggplot2) 
library(fitdistrplus)
```

## Preprocessing

The preprocessing step involves removal of fraudulent transactions which might affect the distribution estimate negatively. The total supply of the networkbnb token is 192443301 (quoted from etherscan.io) and the range of subunits for the token is 18 decimal units. Thus any transaction that attempts to log a value greater than the product of total supply and subunits is deemed as fraudulent.

The token networkbnb does not have any fraudulent transactions.

```{r}
file <-'B:/study/Fall 2018/Stats for DS/Project1/Datasets/Ethereum token graphs/networkbnbTX.txt'
col_names <- c("FROMNODE","TONODE","TIME","TOKENAMOUNT")
mydata <- read.csv( file, header = FALSE, sep = " ", dec = ".", col.names = col_names)
amounts <- mydata[4]

totalSupply <- 192443301
subUnits <- 18
totalAmount <- totalSupply * (10 ^ subUnits)
temp <- which(mydata< totalAmount)
#print meta data 
message('Maximum allowed amount : ', totalAmount)
count <- 0
outliers <- 0
for( a in 1:nrow(amounts)){
  if( a > totalAmount){
    outliers <- outliers + 1
  }
  else{
    count <- count + 1
  }
}
message('Number of outliers : ',outliers)
message('Number of valid amounts : ',count)
```

## Calculating selling frequency

```{r pressure, echo=FALSE}
countFromDf <- count(mydata, "FROMNODE")
countFromFf <- count(countFromDf, "freq")
colnames(countFromFf) <- c("Users_Count", "Sell_Count")
head(countFromFf)
descdist(countFromFf$Sell_Count, boot= 500)
```

## Approximating the selling distributions

From the above Cullen and Frey graph we could narrow down our distribution selection to Weibull, lognormal, gamma and poisson.
```{r}
distributionFit_Seller_pois <- fitdist(countFromFf$Sell_Count, "pois", method ="mle")
distributionFit_Seller_wb <- fitdist(countFromFf$Sell_Count, "weibull", method ="mle")
distributionFit_Seller_ln <- fitdist(countFromFf$Sell_Count, "lnorm", method ="mle")
distributionFit_Seller_gm <- fitdist(countFromFf$Sell_Count, "gamma" ,method="mme")
distributionFit_Seller_wb
plot(distributionFit_Seller_wb)
distributionFit_Seller_pois
plot(distributionFit_Seller_pois)
distributionFit_Seller_ln
plot(distributionFit_Seller_ln)
distributionFit_Seller_gm
plot(distributionFit_Seller_gm)
```
##Calculating the buying frequency
```{r}
countToDf <- count(mydata, "TONODE")
countToFf <- count(countToDf, "freq")
colnames(countToFf) <- c("Users_Count", "Buy_Count")
head(countToFf)
descdist(countToFf$Buy_Count, boot=500)
```
##Approximating the buying distributions
```{r}
distributionFit_Buyer_pois <- fitdist(countToFf$Buy_Count, "pois", method ="mle")
distributionFit_Buyer_wb <- fitdist(countToFf$Buy_Count, "weibull", method ="mle")
distributionFit_Buyer_ln <- fitdist(countToFf$Buy_Count, "lnorm", method ="mle")
distributionFit_Buyer_gm <- fitdist(countToFf$Buy_Count, "gamma", method ="mme")

distributionFit_Buyer_pois
plot(distributionFit_Buyer_pois)
distributionFit_Buyer_wb
plot(distributionFit_Buyer_wb)
distributionFit_Buyer_ln
plot(distributionFit_Buyer_ln)
distributionFit_Buyer_gm
plot(distributionFit_Buyer_gm)
```

##Conclusion